\documentclass[a4paper]{mcdowellcv}

\usepackage{amsmath}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	urlcolor=blue!60!black
}

\name{Tudor-Adrian Nazarie}
\address{+44 7445708404 \linebreak \href{mailto:tudor@nazarie.net}{tudor@nazarie.net}}
\contacts{London, \linebreak United Kingdom}

\begin{document}

\makeheader

\begin{cvsection}{Work Experience}

	\begin{cvsubsection}{Full Stack Engineer/DevOps}{Solidatus}{Fall 2022 -- Present}
		\begin{itemize}
			\item Contributed to the development of a world-class data lineage and data management software.
			\item Worked on both front-end and back-end features for a modern, enterprise-grade web application.
			\item Improved and maintained the infrastructure supporting the development team, as needed.
			\item Was responsible for deploying and maintaining a fleet of different cloud services supporting the business.
			\item Designed, developed, and deployed an automated pipeline for gathering metrics and logs from production
			      environments, used to develop crucial business and pricing strategies.
			\item Maintained and improved the CI/CD pipeline for the development team, from code commit to deployment.
			\item Technologies used:
			      \begin{itemize}
				      \item Software development: \textbf{ASP.NET Core (C\#), React (TypeScript), CSS, SASS, Rust, Bash}
				      \item Cloud infrastructure: \textbf{Google Cloud Platform, Kubernetes, Terraform, Docker}
				      \item CI/CD: \textbf{GitHub Actions, JetBrains TeamCity}
			      \end{itemize}
		\end{itemize}
	\end{cvsubsection}

	\begin{cvsubsection}{Quantitative Technologist}{Qube Research \& Technologies}{Apr 2021 -- Sep 2021}
		\begin{itemize}
			\item 6 month industry placement as part of my master's degree at Imperial College London.
			\item Developed, implemented, and packaged an automated test harness to aid in \textbf{low latency testing},
			      based on a server-worker architecture.
			\item Developed a console based application for monitoring cache sage and misses on a per-core and per-process
			      for Intel processors, using official Intel APIs.
			\item Maintained constant communication with both the trading team as well as the technical team to develop and
			      test new ideas, aiming to increase performance of low latency, high frequency trading strategies.
			\item Technologies used: \textbf{Flask (Python), React (TypeScript), C++, RHEL (RPM packaging)}
		\end{itemize}
	\end{cvsubsection}

	\begin{cvsubsection}{Computer Scientist}{Netcraft}{Jul 2019 -- Oct 2020}
		\begin{itemize}
			\item Experience split over the course of three internships.
			\item Maintained and extended the company's \textbf{anti-phishing} take down solution.
			\item Helped develop an anti-phishing native Android application.
			\item Technologies used: \textbf{PHP, Perl, Java (Android)}
		\end{itemize}
	\end{cvsubsection}

\end{cvsection}

\begin{cvsection}{Education}

	\begin{cvsubsection}{MEng Computing (Artificial Intelligence)}{Imperial College London}{2018 -- 2022}
		\begin{itemize}
			\item Graduated with Upper Second Class Honours.
			\item Undergraduate courseworks: Pintos (Operating Systems module), WACC (Compilers module)
			\item Fourth year personal project title: \textbf{``Automated Adversary Emulation using Reinforcement Learning''}.
		\end{itemize}
	\end{cvsubsection}

\end{cvsection}

\begin{cvsection}{Skills \& Technologies}
	\begin{cvsubsection}{}{}{}
		\begin{itemize}
			\item Programming languages: \textbf{C\#, TypeScript, Rust, JavaScript, Kotlin, Java, Python}
			\item Web development: \textbf{ASP.NET Core, React, HTML, CSS, SASS}
			\item Cloud infrastructure: \textbf{Google Cloud Platform, Microsoft Azure, Terraform, Kubernetes, Docker}
			\item Linux system administration: \textbf{RHEL, Ubuntu, shell scripting, RPM/DEB packaging}
			\item Database management systems: \textbf{MongoDB, PostgreSQL, MySQL}
			\item Software development:
			      \begin{itemize}
				      \item Able to write high-quality code, using appropriate technologies and tools, libraries,
				            and algorithms.
				      \item Able to integrate in software development teams and to adapt to the team's workflow.
				      \item Used to working with common collaboration tools common in software development such as \textbf{Git,
					            Kanban boards (YouTrack), and online code review tools}.
			      \end{itemize}
			\item Languages:
			      \begin{itemize}
				      \item \textbf{English} (fluent)
				      \item \textbf{Romanian} (native)
			      \end{itemize}
		\end{itemize}
	\end{cvsubsection}
\end{cvsection}

\end{document}
